### 2024-07-09 Scripts/Manuscript/manuscript.Rmd
altered the reliability reporting diagram.

```{r ReliabilityReportingFlowDiagram, fig.cap = "Reliability reporting flow diagram. Figure shows the number of measures as reported in both the replication protocols and original article, which meet the criterion in the box within the diagram and those criteria before it."}
knitr::include_graphics(path = "../../SupplementaryMaterials/reliability_reporting_flow_diagram.png")
```

>>>>

```{r ReliabilityReportingFlowDiagram, fig.cap = "Reliability reporting flow diagram. Figure shows the number of measures as reported in both the replication protocols and original article, which meet the criterion in the box within the diagram and those criteria before it.", out.height = "60%"}
knitr::include_graphics(path = "../../SupplementaryMaterials/reliability_reporting_flow_diagram.png")
```
